Fusion Moves for Correlation Clustering

### 2014-10-27 paper/egpaper_for_review.tex
added notation
shift theorems
contradict graph
polyherdal section

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}

@@

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}

@@

@@

\begin{theorem}[NameMe]
Solving ??? on the contracted graph is 
equivalent to solving ??? on the 
original graph with additional 
must link constraints
\end{theorem}

\begin{proof}[Proof of theorem ]
todo
\end{proof}

\begin{theorem}[NameMe]
Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{new}$ the solution of \ref{???}.
$x_{new}$  will never decrease the energy:
$x_{new} \cdot w \leq  \min( x_{a}\cdot w,  x_{b}\cdot w) $ 
\end{theorem}

\begin{proof}[Proof of theorem ]
todo
\end{proof}

\begin{theorem}[NameMe]

Let $x_{a}$ and $x_{b}$ be two proposal solutions and  $x_{opt}$ the global solution,
$X_{a}^c, X_{b}^c$ and $ X_{opt}^c$ the set of cut edges in  $x_{a}, x_{b}$  and $ x_{opt}$
optimal solution.
Iff  $ X_{opt}^c \subseteq  (X_{a}^c \cup X_{b}^c)$,  the solution of \ref{???} will be $x_{opt}$.
\end{theorem}

\begin{proof}[Proof of of theorem]
todo
\end{proof}

@@

\subsection{Polyhedral Interpretation}
\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
}
\end{figure}

>>>>

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

@@

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\newcommand{\OR}{\textrm{ or }}

@@

\paragraph{Our Notation}
$G$ Graph.
$V$ Set of Nodes.
$E$ Set of Edges.
$l$ node label.
$y$ edge label.
$w$ edge weight
$MC(G)$ multicut polytope
$P(G)$ the set of valid edge labeling (MC(G) is convex hull of P(G))
$y^*$ for opt. labeling
$G_y=(V_y,E_y)$ contradiction of graph $G$ with respect to $y$

@@

@@

\subsection{Properties and Polyhedral Interpretation}
An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
In each iteration the current and proposed segmentation define an inner polyheadral 
approximation of the original multicut polytope. 
Optimizing over this polytope is the same problem as the original one, but much smaller.
Furthermore, the costs does not change and and improvement in the smaller polytope will 
be the same in the original graph.
The choice of the proposal defines the shape of the auxiliary polytope. 
In the given toy example, the first (red) polytope give a huge improvement, the second proposal
defines the blue polytope which does not lead to an improvement. 
The third proposal generates the green polytope that includes the global optimal solution.

This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
}
\label{fig:polyheadral}
\end{figure}

\begin{theorem}[Equivalence]
The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
with additional must link constraints ($y^* \leq y$).
%
\begin{proof}
Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
\end{proof}
%
\end{theorem}

\begin{theorem}[Monotone]
Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
Than $y^*$  will never decrease the energy:
$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
%
\begin{proof}
The feasible set of the fusion move includes per definition  $y'$ and $y''$.
If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
and that why not the propose segmentation of a fusion.
\end{proof}
%
\end{theorem}

\begin{remark}[Fix-point]
Let $Y$ be the set of possible proposals, than
$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
\end{remark}

\begin{remark}[Optimality]
Let $y'$ be the current and $y''$ the proposed segmentation.
If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
\end{remark}
